%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/jacktgriffiths/}{\Large Jack Griffiths}} & Email : \href{mailto:x8i47@students.keele.ac.uk}{jacktgriffiths@proton.me}\\
  \href{https://www.linkedin.com/in/jacktgriffiths/}{https://www.linkedin.com/in/jacktgriffiths/} & Mobile : +44 7883 730 764 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Keele University}{Keele, UK}
      {Masters of Research in Bioscience (Neuroscience);  Grade: NA}{Sep. 2024 -- Sep. 2025}
    \resumeSubheading
      {Keele University}{Keele, UK}
      {Bachelor of Science in Neuroscience (Hons);  Grade: 2:1 (65)}{Sep. 2022 -- Jun. 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Keele University}{Keele, UK}
      {Graduate Researcher - Neural Tissue Engineering Lab (Dr Chris Adams)}{Jan 2025 - Present}
      \resumeItemListStart
      \resumeItem{Neural Tissue Culture}
          {In progress.}
        \resumeItem{Microelectrode Arrays}
          {In progress.}
      \resumeItemListEnd

      \resumeSubheading
      {Keele University}{Keele, UK}
      {Student Researcher - Neuroscience}{Jan 2025 - Present}
      \resumeItemListStart
      \resumeItem{Systematic Review}
          {"The Efficacy of Psilocybin in the Treatment of Major Depressive Disorder (MDD): A Systematic Review"}
      \resumeItemListEnd

    \resumeSubheading
      {Mail Solutions Group}{Telford, UK}
      {Project Manager - Headed up new start-up eco-friendly products division}{Dec. 2018 - Sep. 2021}
      \resumeItemListStart
      \resumeItem{International Research}
          {Organised and facilitated an international research trip to China, collaborating with manufacturers and suppliers to establish key partnerships.}
        \resumeItem{Investment}
          {Grew the division from start-up to £300,000 turnover and secured a further £500,000 in investment into world-leading machinery, the first of its kind in the UK, projecting a £1,500,000 turnover.}
        \resumeItem{BRC-Accredited Facility}
          {Planned and oversaw the construction of a BRC-certified food packaging manufacturing facility (360m\textsuperscript{2}).}
           \resumeItem{Team Leadership}
          {Planned and constructed a BRC-approved food packaging manufacturing facility (360m\textsuperscript{2}).}
          \resumeItem{Client Relations}
          {Built strong relationships with customers across the UK, Europe, and the Middle East.}
           \resumeItem{Sales Strategy}
          {Collaborated with the Sales Director to create targeted sales plans and drive lead generation. }
           \resumeItem{Team Expansion}
          {Recruited and onboarded six employees, establishing an efficient 18/6 work schedule.}
      \resumeItemListEnd

    \resumeSubheading
      {Capgemini}{Telford, UK}
      {Software Engineer - HMRC Aspire Project}{Nov. 2015 - Sep. 2018}
      \resumeItemListStart
        \resumeItem{Big Data Integration}
          {Gained extensive experience in resolving challenges related to ingesting standardised and non-standardized data into a centralised Big Data hub.}
          \resumeItem{Data Ingestion and Processing}
          {Developed and executed Pentaho scripts to ingest and interpret HMRC taxpayer data efficiently. Extracted and processed data using MySQL, Impala, and Beeline for accurate analysis.}
          \resumeItem{Java Development}
          {Supported the development and documentation of our in-house bespoke standardisation solution.}
          \resumeItem{Git Administrator}
          {Took ownership of administering Bitbucket, the git solution used for storing all company project data.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Capgemini}{Telford, UK}
      {Data Scientist - McDonald's Project}{Sep. 2018 - Dec. 2018}
      \resumeItemListStart
        \resumeItem{Big Data Implementation}
          {Contributed to McDonald’s pilot Big Data and Analytics project, implementing advanced technologies such as Paxata and Waterline Data to optimise data processing. Conceptualized and prepared large-scale datasets for big data analysis, ensuring seamless integration with new technologies.}  
    \resumeItem{Training}
          {Delivered training sessions on Paxata and Waterline Data, equipping analysts to manage and process McDonald’s vast datasets effectively.}  
    \resumeItem{Technical Documentation}
          {Developed comprehensive documentation to support the McDonald’s business analytics team in adopting new tools. }
          \resumeItem{Stakeholder Collaboration}
          {Liaised with managers and clients to facilitate the successful handover and adoption of new technologies.}
        \resumeItem{Certification}
          {Earned certification as a Paxata Data Analyst, demonstrating technical expertise in big data analytics tools.}
      \resumeItemListEnd

    \resumeSubheading
      {Logicomm 2000}{Cannock, UK}
      {Computer Engineer - Apprenticeship}{Sep. 2014 - Nov. 2015}
      \resumeItemListStart
        \resumeItem{Server and Network Deployment}
          {Implemented server stacks, including Active Directory and Exchange services, and optimised customer networks with CAT 5e/CAT 6 cabling, firewall, and router configurations.}
                  \resumeItem{Technical Support}
          {Provided cross-platform support for Windows, Mac, and Linux, including remote assistance via ScreenConnect and hardware deployment for customer needs.}
                  \resumeItem{Wi-Fi and Connectivity}
          {Installed long-distance Wi-Fi bridges using Ubiquiti systems to extend reliable connectivity.}
                  \resumeItem{Web and Task Management}
          {Designed and edited customer websites while managing support tickets using Spiceworks for efficient task tracking.}
      \resumeItemListEnd
      

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, Javascript, C++, SQL, Java}
     \hfill
     \textbf{Technologies}{: }
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
